---
title: "quiz"
format: html
editor: visual
---

## 

```{r}

couple_Student_one <- rnorm(100, mean = 25, sd = 5)
couple_Student_two <- rnorm(100, mean = couple_Student_one + 5, sd = 5)
student_three <- rnorm(100, mean = 20, sd = 5)
student_four <- rnorm(100, mean = 25, sd = 5)
student_five <- rnorm(100, mean = 30, sd = 5)


data <- data.frame(
 couple_Student_one = couple_Student_one,
  couple_Student_two = couple_Student_two,
  student_three  = student_three ,
  student_four = student_four,
  student_five = student_five
)


head(data)

```

To test if there exist the null value in the data.

```{r}
any(is.na(data))


```

get the result of the unique from data.

```{r}
unique(data)
```

Testing to make sure there exist five students to participant this activities.

```{r}
ncol(data)
```

To find is there any duplicate rows to be found.

```{r}
if (!any(duplicated(data))) {
  print("No duplicate rows found.")
} else {
  print("Contain the duplicate rows.")
}
```

Test the value whether is the normal.

```{r}
for (i in 2:ncol(data)) {
  if (shapiro.test(data[,i])$p.value >= 0.05) {
    print(paste("The Column", colnames(data)[i], "is normal."))
  } else {
    print(paste("oops ! Failed for column", colnames(data)[i], "."))
  }
}
```

I made different color based on the people in the couple group.

```{r}

ggplot(data, aes(x = couple_Student_one, y = couple_Student_two, color = "Group 1")) +
  geom_point(size = 3) +
  scale_color_manual(values = c("Group 1" = "red")) +
  labs(x = "Student One", y = "Student Two", color = "Group") +
  ggtitle("Relationship between Student One and Student Two") +
  theme_minimal()
```

Now, there is the relation of the student_three , student_four, student_five. (The density graph)

```{r}
library(ggplot2)


df <- data.frame(
  value = c(data$student_three, data$student_four, data$student_five),
  group = rep(c("Student Three", "Student Four", "Student Five"), each = 100)
)


ggplot(df, aes(x = value, fill = group)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Student Three" = "black", "Student Four" = "blue", "Student Five" = "pink")) +
  labs(x = "Value", y = "Density", title = "Density Plot of Student Scores")

```
